---
title: "SAIGEQTL: Quick Start Guide"
author:
- name: Wei Zhou
- name: Anna Cuomo
- name: Linfeng Hu
date: "`r Sys.Date()`"
output:
  BiocStyle::html_document:
    toc: true
    toc_depth: 2
vignette: >
  %\VignetteIndexEntry{SAIGEQTL: Quick Start Guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = TRUE,
    eval = FALSE,
    message = FALSE,
    warning = FALSE
)
```

# Introduction

SAIGEQTL implements the Scalable and Accurate Implementation of Generalized
Poisson mixed model for expression quantitative trait locus (eQTL) mapping
at the single-cell level.

This vignette provides a quick start guide to using SAIGEQTL for eQTL
analysis.

## Installation

```{r install, eval=FALSE}
# From Bioconductor (when available)
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("SAIGEQTL")
```

## Loading the Package

```{r load}
library(SAIGEQTL)
```

# Workflow Overview

A typical SAIGEQTL analysis consists of two main steps:

1. **Fit the null model** using `fitNULLGLMM_multiV()`
2. **Perform association testing** using `SPAGMMATtest()`

## Step 1: Fit the Null Model

The null model accounts for population structure and relatedness using a
genetic relationship matrix (GRM).

```{r fit-null, eval=FALSE}
# Example: Fit null model
# fitNULLGLMM_multiV(
#     phenoFile = "phenotype.txt",
#     phenoCol = "expression",
#     covarColList = c("age", "sex", "PC1", "PC2"),
#     sampleIDColinphenoFile = "sample_id",
#     ...
# )
```

## Step 2: Perform Association Testing

After fitting the null model, perform variant-level or region-based
association testing.

```{r test, eval=FALSE}
# Example: Run association test
# SPAGMMATtest(
#     modelFile = "null_model.rda",
#     genoFile = "genotypes.bgen",
#     outputFile = "results.txt",
#     ...
# )
```

# Additional Resources

For detailed documentation and examples, please see:

- Package documentation: `?fitNULLGLMM_multiV`, `?SPAGMMATtest`
- GitHub repository: <https://github.com/weizhou0/SAIGEQTL>

# Session Information

```{r sessionInfo, eval=TRUE}
sessionInfo()
```
